---
title: "Assignment-2"
author: "Amine Ceyda Tandogan"
date: "21/01/2022"
output: word_document
---

# PART 1
```{r include=FALSE}
library(tidyverse)
set.seed(2018555061)
ourdata <- read.csv("covid-data-2020.csv")
newdata <-ourdata[sample(nrow(ourdata),1000,replace = FALSE),]    
newdata
```

## Q1 : Calculate the five-number summary statistics (minimum-Q1-median-Q3-maximum) of covid-19 daily new cases for each country within each month. (you can use quantile() function to get the quartiles)
```{r echo=FALSE,}
question1<-newdata %>% 
  group_by(location,month) %>% 
  summarise(min= min(new_cases),Q1 = quantile(new_cases, 0.25,na.rm=T),median = median(new_cases,na.rm=TRUE),Q3=quantile(new_cases, 0.75,na.rm =T),max= max(new_cases) )
question1
```

## Q2 : Find the highest daily cases and deaths separately for each country. 
```{r echo=FALSE}
question2 <- newdata %>% 
  group_by(location) %>% 
  summarise(max_death=max(new_deaths,na.rm = T),max_case=max(new_cases,na.rm = T))
question2

```

## Q3 : Identify the month in which the mean daily cases is the highest for each country
```{r echo=FALSE}
question3 <- newdata %>% 
  group_by(location,month) %>% 
  summarise(mean_of_dailycases=mean(new_cases,na.rm = T)) %>% 
  filter(mean_of_dailycases==max(mean_of_dailycases))
question3
```

## Q4 : Select 3 country and plot the distribution of daily cases by month. Use location as clusters (i.e., color=location) to show the difference between countries.
```{r echo=F, fig.align='default',fig.cap='Figure 1. The distribution of daily cases by month.'}
question4 <- newdata %>% 
  filter(location == "Estonia" | location == "Andorra" |location == "Belarus")
ggplot(data = question4, mapping = aes(x = month, y = new_cases,color = location) ) +
  geom_boxplot()

```

## PART 2
```{r echo=FALSE}
library(tidyverse)

sample_<-sample(stringr::sentences,size=100)      #random sample of 100 sentences from this data
str<-paste(sample_, collapse=" ")
str<-str_split(str, boundary("word"))[[1]]        # to split these sentences into words 
vector_word<-unlist(str)                          # to take each word as a member of a vector
vector_word<-unique(vector_word)                  #to remove duplicated words
newSdata <-vector_word     #new string data
print("New Data ")
newSdata
```



## Q1 : Find words which are starting with start a and ending with e.
```{r echo=FALSE}
question1 <- tibble(word = newSdata) %>%
  filter (str_detect(newSdata, "^a")  & str_detect (newSdata, "e$"))
print(question1)
```

## Q2 : Calculate the number of words which have more than 3 vowels.
```{r echo=FALSE}
question2 <- tibble(
  word=newSdata,
  vowels=str_count(newSdata, "[aeiou]")
)
question2<-question2 %>% 
  filter(vowels>=3)
print("words with vowel numbers greater than 3")
question2
print("The total number of words with more than 3 vowels in the words:")
print(nrow(question2))

```

## Q3 : List the five longest word in your data
```{r echo=FALSE}
question4 <-newSdata 
question4<-question4[order(nchar(question4),decreasing = T)]
print("5 Longest word in my data:")
question4[1:5]

```

## Q4 : Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.
```{r echo=FALSE}
question4 <- tibble(word = newSdata) %>%
  filter (str_detect(newSdata, "age")|str_detect (newSdata, "any")|str_detect (newSdata, "day")|str_detect (newSdata, "exp")|str_detect (newSdata,"her")|str_detect (newSdata, "pro")|str_detect (newSdata, "the"))
print(question4)


```

**Amine Ceyda Tandogan 2018555061 Cen429 morning**

